Twisted \(M\)-theory and its perturbative quantization.

### 2021-01-29 paper.tex
fixed illegal commands and formatting errors

% Created 2020-10-14 Wed 14:51
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}

\usepackage{macros-mtheory}

@@

So, in order to make sense of the action functional $S_{\rm BF} + J$ as a homogenously even functional, the $\ZZ/2$-graded space of fields takes the form
\[
  \begin{array}{ccl}
    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[1] \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
  \end{array}
\]
Here, we have used the following convention for $\ZZ/2$-graded complexes.
If $V$ is a $\ZZ/2$-graded vector space with even part $V^0$ and odd part $V^1$, then $V[1]$ is a $\ZZ/2$-graded vector space with even part $V^1$ and odd part $V^0$.

@@

\begin{conj}
  [Costello-Li \cite{CLsugra}]
  Let $(M,h_{M})$ be a Kahler surface and $(X, h_{X})$ be a Calabi-Yau 4-fold.
  Consider perturbative type IIA supergravity on $M\times X$ around a background where:
  \begin{itemize}
    \item the graviton is set to $h_{M}+ h_{X}$,
    \item the bosonic ghost for local supersymmetries is set to a covariantly constant square-zero spinor $Q$ that is invariant for the $\SU(4)$ subgroup of isometries preserving $X\subset M\times X$,
    \item all other background fields are set to zero.
  \end{itemize}
  In this background, the resulting theory is equivalent to the Kodaira--Spencer type theory whose fields are
  \[
    \Omega^{\bullet}(M) \; \Hat{\otimes} \; \PV^{\bullet, \bullet}(X)[\![u]\!]
  \]
  where $u$ is a parameter of cohomological degree $2$.
  \brian{this theory is only $\ZZ/2$-graded, right?}
  %$L_{\infty}$-structure given by $\ell_{1} = d\otimes 1+ 1\otimes (\dbar+t\partial)$, $\ell_{2} = \wedge\otimes \{-,-\}_{\rm NS}$ and Poisson kernel given by $(1\otimes \partial)\delta_{\Delta(X)}\delta_{\Delta (M)}$.
\end{conj}

@@

Let \(X\) be a Calabi-Yau 4 fold. Minimal Kodaira-Spencer theory on $X$ is a $\Z/2$-graded theory with the following fundamental fields:
\begin{itemize}
\item The even fields are a holomorphic function $\mu^0$ and a $\partial$-closed holomorphic bivector $\mu^2$.
\item The odd fields are a divergence-free holomorphic vector field $\mu^1$ and a $\partial$-closed holomorphic section $\mu^3$ of $\wedge^3 T_X$.
\end{itemize}

The space of fields admits a locally free description obtained by including the ``descendants" \surya{maybe should be more formal here}
The descendants of the field $\mu^j$ will be denoted $u^k \mu^j$ where $k = 1,\ldots, j$.
Here, $u^k \mu^j$ is a section of $\PV^{j - k, \bu}$.
The sheaf of cochain complexes $\cE$ underlying minimal Kodaira--Spencer theory on $X$ is
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
& & & \mu^0 \in \PV^{0,\bu} \\
& & \sum u^k \mu^1 \in \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
& \sum u^k \mu^2 \in  \PV^{2,\bu} \ar[r,"u \partial"] & u \PV^{1,\bu} \ar[r, "u \partial"] & u^2 \PV^{0,\bu} \\
\sum u^k \mu^3 \in \PV^{3,\bu} \ar[r, "u \partial"]& u \PV^{2,\bu} \ar[r,"u \del"] & u^2 \PV^{1,\bu} \ar[r, "u \partial"] & u^3\PV^{0,\bu} \\
\end{tikzcd}
\]
The differential on this sheaf of cochain complexes is given by $\dbar + u \partial$.

There is a local Lie algebra structure on $\Pi\cE$ using the Schouten-Nijenhuis bracket $[-,-]_{\rm Sch}$ on polyvector fields.
On the fields (including the descendants) it is defined by the formula
\[
[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} \{\mu^i, \mu^j\}_{\rm NS} .
\]

The space of fields of minimal Kodaira--Spencer theory $\cE_{\rm KS}$ is equipped with an odd Poisson tensor defined by
\[
\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
\]
Together with the local Lie algebra structure, this data equips $\cE_{\rm KS}$ with the structure of a $\Z/2$-graded Poisson BV theory.

As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory.
The underlying sheaf of cochain complexes is
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
& & & \eta^{0}\in\PV^{0,\bu} \\
& & \mu^{1}+u\mu^{0}\in\PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
u^{-1} \gamma^4 + \gamma^3  \in u^{-1} \PV^{4,\bu} \ar[r, "u \partial"] & \PV^{3,\bu} & &  \\
\beta^{4} \in\PV^{4,\bu} &  &  & \\
\end{tikzcd}
\]
We will again refer to this sheaf as $\cE_{\rm pot}$. Note that we can identify $cE_{\rm pot}\cong \Pi T^{*}(\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu}))$.

\begin{dfn}
  Let $X$ be a Calabi-Yau 4-fold, and let $\mc L$ denote the local dg Lie algebra $\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})$ with Lie bracket given by the Schouten bracket. Kodaira-Spencer with potentials on $X$ is the $\ZZ/2$-graded BV theory given by deforming the BF theory of $\mc L$ by the local functional \[ \frac{1}{3}\int_{X}(\nu^{0}\partial\gamma^{3}\partial\gamma^{3})\]\end{dfn}

@@

\begin{align}
  \PV^{1,\bu}\times\PV^{0,\bu}\to \PV^{0,\bu},\ \ \ & [\mu^{1},\nu^{0}] = \{\mu^{1},\nu^{0}\}_{NS}\\
  \PV^{1,\bu}\times\PV^{1,\bu}\to\PV^{1,\bu},\ \ \ & [\mu^{1}, \mu^{1}] = \{\mu^{1}, \mu^{1}\}_{NS}\\
  \PV{1,\bu}\times u\PV^{0,\bu}\to u\PV^{0,\bu}, \ \ \ & [\mu^{1}, u\mu^{0}]=u\{\mu^{1},\mu^{0}\}_{NS}
  \PV^{3,\bu}\times \PV^{3,\bu}\to \PV^{4,\bu}, \ \ \ & [\gamma^3, \Tilde{\gamma}^3] = \frac{1}{2}(\{\partial \gamma^3 , \Tilde{\gamma}^{3}\}_{\rm NS} +(-1)^{|\gamma^{3}|} \{\gamma^3, \partial \Tilde{\gamma}^{3}\}_{\rm NS}) \\
  \PV^{4,\bu}\times \PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [\beta^{4}, \nu^{0}] = \{\beta^{4}, \nu^{0}\}_{\rm {NS}}\\
  \PV^{3,\bu}\times \PV^{0,\bu}\to \PV^{1,\bu}, \ \ \ & [\gamma^{3}, \nu^{0}] = \{\partial\gamma^{3}, \nu^{0}\}_{\rm NS}\\
  \PV^{3,\bu}\times \PV^{1,\bu}\to \PV^{3,\bu}, \ \ \ & [\gamma^{3}, \mu^{1}] = \{\gamma^{3}, \mu^{1}\}_{\rm NS}\\
  u^{-1}\PV^{4,\bu}\times u\PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [u^{-1}\gamma^{4}, u\mu^{0}] = \{\gamma^{4},\mu^{0}\}_{\rm NS}
\end{align}
\surya{explain more}

>>>>

% Created 2020-10-14 Wed 14:51
% Intended LaTeX compiler: pdflatex
\documentclass[11pt]{amsart}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage{amsfonts}
\usepackage{macros-mtheory}

@@

So, in order to make sense of the action functional $S_{\rm BF} + J$ as a homogenously even functional, the $\ZZ /2$-graded space of fields takes the form
\[
  \begin{array}{ccl}
    \mu = \mu^1+\mu^0 & \in & \left(\pv^{1,\bu}(X)[1] \oplus \pv^{0,\bu}(X) \right) \; \Hat{\otimes} \; \Omega^{\bu}(L) \\
    \gamma = \gamma^0+ \gamma^1 & \in & \left(\Omega^{0,\bu}(X)[1] \oplus \Omega^{1,\bu}(X) \right) \; \Hat{\otimes}\; \Omega^{\bu}(L) .
  \end{array}
\]
Here, we have used the following convention for $\ZZ/2$-graded complexes.
If $V$ is a $\ZZ/2$-graded vector space with even part $V^0$ and odd part $V^1$, then $V[1]$ is a $\ZZ/2$-graded vector space with even part $V^1$ and odd part $V^0$.

@@

\begin{conj}
  [Costello-Li \cite{CLsugra}]
  Let $(M,h_{M})$ be a Kahler surface and $(X, h_{X})$ be a Calabi-Yau 4-fold.
  Consider perturbative type IIA supergravity on $M\times X$ around a background where:
  \begin{itemize}
    \item the graviton is set to $h_{M}+ h_{X}$,
    \item the bosonic ghost for local supersymmetries is set to a covariantly constant square-zero spinor $Q$ that is invariant for the $\rm SU(4)$ subgroup of isometries preserving $X\subset M\times X$,
    \item all other background fields are set to zero.
  \end{itemize}
  In this background, the resulting theory is equivalent to the Kodaira--Spencer type theory whose fields are
  \[
    \Omega^{\bullet}(M) \; \Hat{\otimes} \; \PV^{\bullet, \bullet}(X)[\![u]\!]
  \]
  where $u$ is a parameter of cohomological degree $2$.
  \brian{this theory is only $\ZZ/2$-graded, right?}
  %$L_{\infty}$-structure given by $\ell_{1} = d\otimes 1+ 1\otimes (\dbar+t\partial)$, $\ell_{2} = \wedge\otimes \{-,-\}_{\rm NS}$ and Poisson kernel given by $(1\otimes \partial)\delta_{\Delta(X)}\delta_{\Delta (M)}$.
\end{conj}

@@

Let \(X\) be a Calabi-Yau 4 fold. Minimal Kodaira-Spencer theory on $X$ is a $\ZZ/2$-graded theory with the following fundamental fields:
\begin{itemize}
\item The even fields are a holomorphic function $\mu^0$ and a $\partial$-closed holomorphic bivector $\mu^2$.
\item The odd fields are a divergence-free holomorphic vector field $\mu^1$ and a $\partial$-closed holomorphic section $\mu^3$ of $\wedge^3 T_X$.
\end{itemize}

The space of fields admits a locally free description obtained by including the ``descendants". The descendants of the field $\mu^j$ will be denoted $u^k \mu^j$ where $k = 1,\ldots, j$.
Here, $u^k \mu^j$ is a section of $\PV^{j - k, \bu}$.
The sheaf of cochain complexes $\cE$ underlying minimal Kodaira--Spencer theory on $X$ is
\[\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
& & & \mu^0 \in \PV^{0,\bu} \\
& & \sum u^k \mu^1 \in \PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
& \sum u^k \mu^2 \in  \PV^{2,\bu} \ar[r,"u \partial"] & u \PV^{1,\bu} \ar[r, "u \partial"] & u^2 \PV^{0,\bu} \\
\sum u^k \mu^3 \in \PV^{3,\bu} \ar[r, "u \partial"]& u \PV^{2,\bu} \ar[r,"u \partial"] & u^2 \PV^{1,\bu} \ar[r, "u \partial"] & u^3\PV^{0,\bu} \\
\end{tikzcd}
\]
The differential on this sheaf of cochain complexes is given by $\dbar + u \partial$.

There is a local Lie algebra structure on $\Pi\cE$ using the Schouten-Nijenhuis bracket $[-,-]_{\rm Sch}$ on polyvector fields.
On the fields (including the descendants) it is defined by the formula
\[
[u^k \mu^i , u^\ell \mu^j] = u^{k+\ell} \{\mu^i, \mu^j\}_{\rm NS}.
\]

The space of fields of minimal Kodaira--Spencer theory $\cE_{\rm KS}$ is equipped with an odd Poisson tensor defined by
\[
\Pi_{\rm KS} = (\partial \otimes 1) \delta_{\rm Diag} .
\]
Together with the local Lie algebra structure, this data equips $\cE_{\rm KS}$ with the structure of a $\ZZ/2$-graded Poisson BV theory.

As in the surface case, there is a closely related BV theory describing the "potentials" of minimal Kodaira--Spencer theory. The underlying sheaf of cochain complexes is
\[
\begin{tikzcd}
\ul{\rm odd} & \ul{\rm even} & \ul{\rm odd} & \ul{\rm even} \\
& & & \eta^{0}\in\PV^{0,\bu} \\
& & \mu^{1}+u\mu^{0}\in\PV^{1,\bu} \ar[r, "u \partial"] & u \PV^{0,\bu} \\
u^{-1} \gamma^4 + \gamma^3  \in u^{-1} \PV^{4,\bu} \ar[r, "u \partial"] & \PV^{3,\bu} & &  \\
\beta^{4} \in\PV^{4,\bu} &  &  & \\
\end{tikzcd}
\]
We will again refer to this sheaf as $\cE_{\rm pot}$. Note that we can identify \[\cE_{\rm pot}\cong \Pi T^{*}(\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})).\]

\begin{dfn}
  Let $X$ be a Calabi-Yau 4-fold, and let $\cL$ denote the local dg Lie algebra $\PV^{0,\bu}\oplus (\PV^{1,\bu}\to u\PV^{0,\bu})$ with Lie bracket given by the Schouten bracket. Kodaira-Spencer with potentials on $X$ is the $\ZZ/2$-graded BV theory given by deforming the BF theory of $\cL$ by the local functional \[ \frac{1}{3}\int_{X}(\nu^{0}\partial\gamma^{3}\partial\gamma^{3})\]\end{dfn}

@@

\begin{align}
  \PV^{1,\bu}\times\PV^{0,\bu}\to \PV^{0,\bu},\ \ \ & [\mu^{1},\nu^{0}] = \{\mu^{1},\nu^{0}\}_{NS}\\
  \PV^{1,\bu}\times\PV^{1,\bu}\to\PV^{1,\bu},\ \ \ & [\mu^{1}, \mu^{1}] = \{\mu^{1}, \mu^{1}\}_{NS}\\
  \PV{1,\bu}\times u\PV^{0,\bu}\to u\PV^{0,\bu}, \ \ \ & [\mu^{1}, u\mu^{0}]=u\{\mu^{1},\mu^{0}\}_{NS} \\
  \PV^{3,\bu}\times \PV^{3,\bu}\to \PV^{4,\bu}, \ \ \ & [\gamma^3, \Tilde{\gamma}^3] = \frac{1}{2}(\{\partial \gamma^3 , \Tilde{\gamma}^{3}\}_{\rm NS} +(-1)^{|\gamma^{3}|} \{\gamma^3, \partial \Tilde{\gamma}^{3}\}_{\rm NS}) \\
  \PV^{4,\bu}\times \PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [\beta^{4}, \nu^{0}] = \{\beta^{4}, \nu^{0}\}_{\rm {NS}}\\
  \PV^{3,\bu}\times \PV^{0,\bu}\to \PV^{1,\bu}, \ \ \ & [\gamma^{3}, \nu^{0}] = \{\partial\gamma^{3}, \nu^{0}\}_{\rm NS}\\
  \PV^{3,\bu}\times \PV^{1,\bu}\to \PV^{3,\bu}, \ \ \ & [\gamma^{3}, \mu^{1}] = \{\gamma^{3}, \mu^{1}\}_{\rm NS}\\
  u^{-1}\PV^{4,\bu}\times u\PV^{0,\bu}\to \PV^{3,\bu}, \ \ \ & [u^{-1}\gamma^{4}, u\mu^{0}] = \{\gamma^{4},\mu^{0}\}_{\rm NS}
\end{align}
